### 2013-09-13 background.tex
Kirema seg methods included, and converting background refs, but question about numbers

\subsection{Clinical Background and Significance}
Prostate cancer (PCa) is the most common noncutaneous malignancy among men in the United States. Approximately 1 in every 6 men will develop PCa during their lifetime, with the median age of diagnosis at 67. 1It is also the second leading cause of cancer related death, with 1 in 36 men dying from the disease. The National Cancer Institute estimates that 238,590 men will be diagnosed with PCa in 2013 and 29,720 will die from the disease.1

@@

PCa screening has led to earlier diagnosis of smaller tumors and more localized disease.  However, it is well known that the sensitivity and specificity of PSA and DRE are not optimal. In addition, DRE has a low predictive value at lower PSA ranges, and PSA yields many false positives.2-4 As such, a theoretical risk of over-diagnosis and treatment of low-grade—and possibly clinically insignificant—disease exists. Moreover, due to the random nature of biopsies, cancer located outside the routine sampling site can be missed and the extent of the cancer might be underestimated.3 5 For example, in a study by Mufarrij et al 45.9\%-47.2\% of patients who were candidates for active surveillance but underwent radical prostatectomy had a higher Gleason score on final histopathology than after TRUS biopsy.6 These inaccuracies may lead to inappropriate diagnosis, imprecise risk assessment and potentially avoidable morbidity.

>>>>

\subsection{Clinical Background and Significance}
Prostate cancer (PCa) is the most common noncutaneous malignancy among men in
the United States. Approximately 1 in every 6 men will develop PCa during their
lifetime, with the median age of diagnosis at 67. 1It is also the second
leading cause of cancer related death, with 1 in 36 men dying from the disease.
The National Cancer Institute estimates that 238,590 men will be diagnosed with
PCa in 2013 and 29,720 will die from the disease.~\cite{Howlader2010}

@@

PCa screening has led to earlier diagnosis of smaller tumors and more localized
disease.  However, it is well known that the sensitivity and specificity of PSA
and DRE are not optimal. In addition, DRE has a low predictive value at lower
PSA ranges, and PSA yields many false
positives.~\cite{Howlader2010,Schroder2000,Gosselaar2006} As such, a
theoretical risk of over-diagnosis and treatment of low-grade—and possibly
clinically insignificant—disease exists. Moreover, due to the random nature of
biopsies, cancer located outside the routine sampling site can be missed and
the extent of the cancer might be underestimated.~\cite{Schroder2000,Gupta2013}
For example, in a study by Mufarrij et al. 45.9--47.2\% of patients who were
candidates for active surveillance but underwent radical prostatectomy had a
higher Gleason score on final histopathology than after TRUS
biopsy.~\cite{Mufarrih2010} These inaccuracies may lead to inappropriate
diagnosis, imprecise risk assessment and potentially avoidable morbidity.
